scRNAseq

### 2018-02-21 datasets/scrnaseq/scRNAseq-latest.Rmd
AS:fixed typos

```{r, filenames}
h_wilcox_dat1="h_data_wilcox_p.rds"
h_wilcox_dat2="h_data_wilcox_p_GSE84465.rds"
m_wilcox_dat1="m_data_wilcox_p_GSE45719.rds"
m_wilcox_dat2="m_data_wilcox_p_GSE94383.rds"

@@

g_data_sub=readRDS("h_g_nofilter_subdata.rds")
groups=c(rep(1,(dim(g_data_sub)[2]/2)),rep(2,(dim(g_data_sub)[2]/2)))
compute_wilcoxde_sc(g_data_sub,h_wilcox_dat1,groups)

@@

```{r, mastcov, fig.width=10, fig.height=7}
print("human_plate_1")
hmast1 <- plot_covariate_diagnostics(paste0(,h_mast_dat1),"mast",h_cov)
print(hmast1$plot)

>>>>

```{r, filenames}
h_wilcox_dat1="h_data_wilcox_p_GSE63818-GPL16791.rds"
h_wilcox_dat2="h_data_wilcox_p_GSE84465.rds"
m_wilcox_dat1="m_data_wilcox_p_GSE45719.rds"
m_wilcox_dat2="m_data_wilcox_p_GSE94383.rds"

@@

g_data_sub=readRDS("h_g_nofilter_subdata_GSE63818-GPL16791.rds")
groups=c(rep(1,(dim(g_data_sub)[2]/2)),rep(2,(dim(g_data_sub)[2]/2)))
compute_wilcoxde_sc(g_data_sub,h_wilcox_dat1,groups)

@@

```{r, mastcov, fig.width=10, fig.height=7}
print("human_plate_1")
hmast1 <- plot_covariate_diagnostics(paste0(h_mast_dat1),"mast",h_cov)
print(hmast1$plot)
